Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
minor edit to 4th idea of pf, 3rd idea of pf

\item[(c)] Let $\tau = \max(1,
	\max_{1 \leq i \leq m}(\deg(x_i)))$. Then, $R_\halfcan$ is generated over $R_\halfcan'$
	in degrees up to $\beta$ with $I$ generated over $I'$ in
	degrees up to $\max(2 \beta, \beta + \tau).$
\end{enumerate}
\end{lem}

@@

\sssec*{Idea of Proof:}
We check the theorem in two cases, depending on whether $\Delta > 0$.
If $\Delta > 0$, we first check that the theorem holds for $L_X$
by adding in log points, and then check it holds for $L$ by raising
the stabilizer orders of stacky points in a sequence of steps. When
raising the stacky orders, it is important that we increment the
stabilizer orders of the maximum possible number of stacky points
at each step, so that the corresponding set will remain admissible.
The check for $\Delta = 0$ is similar, although in this case we do
not need to add in log points, only stacky points, and we will need
to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.

>>>>

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
	in degrees at most $\beta$ with $I$ generated over $I'$ in
	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
	\max_{1 \leq i \leq m}(\deg(x_i)))$).
\end{enumerate}
\end{lem}

@@

\sssec*{Idea of Proof:}
We check the theorem in two cases, depending on whether $\Delta > 0$.
If $\Delta > 0$, we first check that the theorem holds for $\halfcan_X$
by inductively adding in log points to the base case of $\halfcan_X'
= 0$. Then we check that it holds for $\halfcan$ by raising
the stabilizer orders of stacky points in a sequence of steps. When
raising the stacky orders, it is important that we increment the
stabilizer orders of the maximum possible number of stacky points
at each step, so that the corresponding set will remain admissible.
The check for $\Delta = 0$ is similar, although in this case we do
not need to add in log points, only stacky points, and we will need
to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.
